Interval Probability for Fuzzy Quantum Theories

### 2016-07-14 prob.tex
From: Tai, Yu-Tsung Sent: Thursday, July 14, 2016 9:33 To: Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu> Subject: RE: progress?
Updated the example for {impossible, unlikely, likely, certain}, and the
relation between Radon-Nikodym derivative and the Born rule…

To Andy, should I add labels on vectors in the figure produced by
Mathematica? I didn’t find command to add labels in Graph3D through…
Thanks.

Best regards, 
Tai, Yu-Tsung (戴淯琮)
PhD student in Mathematics & Computer Science
Indiana University, Bloomington

From: Hans

Actually, constructing a quantum probability measures from a density
matrix~$\rho$ is similar to defining a classical probability measure
by its Radon-Nikodym derivative. This can be seen more easily if we
pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\psi_{j}\in S}}\proj{\psi_{j}}$,
where $S$ is the linear subspace $P$ projects onto. Then, a density
matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\proj{\psi_{j}}$,
and the Born rule becomes
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\psi_{j}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
\end{eqnarray}
which is basically the same as equation (\ref{eq:Radon-Nikodym}).

>>>>

Actually, constructing a quantum probability measures from a density
matrix~$\rho$ is similar to defining a classical probability measure
by its Radon-Nikodym derivative. This can be seen more easily if we
pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in S}}\proj{\psi_{j}}$,
where $S$ is the linear subspace $P$ projects onto. Then, a density
matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$,
and the Born rule becomes
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\ket{\psi_{j}}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
\end{eqnarray}
which is basically the same as equation (\ref{eq:Radon-Nikodym}).
